Supplementary materials for ``Inattentive responding can induce spurious associations between task behavior and symptom measures''

### 2023-04-10 manuscripts/supp.tex
checkpointing manuscript progress

\begin{figure}[H]
    \includegraphics[width=17cm]{../figures/supp_01.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Signed Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions. (A) No Screening = no exclusions ($N=386$). (B) Accuracy Only = exclusions based on chance-level performance in the reversal-learning task ($N=352$). (C) Infrequency Only = exclusions based on invalid or improbable responses to infrequency items ($N=301$). (D) Both Types = exclusions based on the previous two measures ($N=283$). Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons). Black Xs indicate significant correlations ablated under screening. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
    \label{fig:figS01}
\end{figure}

\clearpage
\subsection*{Bootstrapping Analysis}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_02.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{The pattern of significant behavior-symptom correlations before (A; $N=386$) and after (B; $N=301$) screening compared to the resulting pattern when random subsets of participants ($N=301$, matched to screening using the infrequency measure) are removed (C). Panels (A) and (B) are reproduced from Figure 4 for convenience. (C) The fraction of significant correlations in 5000 bootstrapped samples. (D) The similarity of the pattern of correlations after removal of random subsets to that before and after screening using the infrequency measure ($N=5000$ bootstrapped samples). Similarity was calculated using the simple matching coefficient. Random removal subsets were significantly more similar to the ``No Screening" than to the ``Infrequency" screening datasets (two-tailed, paired-samples $t$-test: $t = 262.490$, $p < 0.001$, $d = 3.713$, 95\% CI = [0.136, 0.138]).}
    \label{fig:figS02}
\end{figure}

\clearpage
\subsection*{The relationship between sample size and false positive rates generalize to other sets of variables}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_03.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{False positive rates for spurious correlations \emph{increase} with sample size. \textit{Left:} Spearman rank correlations and 95\% bootstrap confidence intervals between inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants. The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size. Markers are jittered along the x-axis for legibility. \textit{Right:} False positive rates for inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants. False positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\beta$ and 7-down was statistically significant. The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
    \label{fig:figS03}
\end{figure}

\clearpage
\subsection*{The relationship between sample size and true positive rates for true correlations}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_04.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{True correlations are independent of the proportion of C/IE participants in the sample. \textit{Left:} Spearman rank correlations and 95\% bootstrap confidence intervals between learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants. The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size. Markers are jittered along the x-axis for legibility. \textit{Right:} True positive rates for learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants. True positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\kappa$ and GAD-7 was statistically significant. The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
    \label{fig:figS04}
\end{figure}

@@

\subsection*{Posterior predictive checks}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_05.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Posterior predictive checks for the risk-sensitive temporal difference learning model. (A) Observed (black) and predicted (blue) learning curves averaged across the group ($N=375$). (B) Observed versus predicted choice accuracy across participants ($N=375$). (C) Distribution of average predictive density across participants ($N=375$).}
    \label{fig:figS05}
\end{figure}

\clearpage
\subsection*{Participant demographics}
\begin{table}[!h]
    \centering
    \small
    \setlength{\tabcolsep}{15pt}
    \begin{tabular}{ rrrrr }
        \toprule
        & \multicolumn{2}{c}{MTurk} & \multicolumn{2}{c}{Prolific} \\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        Total & \multicolumn{2}{c}{N=186} & \multicolumn{2}{c}{N=200} \\
        \midrule
        Age & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        18-25   &      16 &   8.6 &       78 &  39.0 \\
        26-35   &      76 &  40.9 &       69 &  34.5 \\
        36-45   &      46 &  24.7 &       31 &  15.5 \\
        46-55   &      22 &  11.8 &       13 &   6.5 \\
        55+     &      26 &  14.0 &        9 &   4.5 \\
        \midrule
        Gender & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Female             &    83 &  44.6 &    112 &  56.0 \\
        Male               &   103 &  55.4 &     85 &  42.5 \\
        Other              &     0 &   0.0 &      3 &   1.5 \\
        \midrule
        Ethnicity & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Hispanic or Latino     &    15 &   8.1 &     10 &   5.0 \\
        Not Hispanic or Latino &   168 &  90.3 &    183 &  91.5 \\
        Rather not say         &     2 &   1.1 &      7 &   3.5 \\
        Unknown                &     1 &   0.5 &      0 &   0.0 \\
        \midrule
        Race & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        African American                 &    21 &  11.3 &      7 &   3.5 \\
        Asian                                     &     5 &   2.7 &     53 &  26.5 \\
        White                                     &   151 &  81.2 &    121 &  60.5 \\
        Multiracial                               &     6 &   3.2 &      4 &   2.0 \\
        Rather not say                            &     1 &   0.5 &     12 &   6.0 \\
        \midrule
        Use other platform & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Yes            &      71 &  38.2 &       28 &  14.0 \\
        No             &     115 &  61.8 &      172 &  86.0 \\
        \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{The demographics of each sample by online labor market. On average, the samples were similar though the sample from Mechanical Turk was older (two-tailed, two-sample $t$-test: $t(384)=6.567$, $p<0.001$, $d=0.669$, 95\% CI = [5.4, 10.0]) and comprised of fewer women (two-tailed, two-sample proportions test: $z(384)=2.529$, $p=0.011$, $h=0.258$, 95\% CI = [0.030, 0.228]). Note: the demographics do not include 20 participants excluded for participating in the study twice, once per platform.}
    \label{tab:tabS01}
\end{table}

\clearpage
\subsection*{Careless participants show different behaviors on the reversal learning task}
\begin{table}[H]
    \centering
    \begin{tabular}{lcccccc}
    \toprule
    {} &  Attentive &    C/IE &   $t$-value &   $p$-value &  Cohen's $D$ & 95\% CI \\
    \midrule
    Acc      &      0.587 &   0.532 &  4.008 &  $<$0.001 &  0.492 &    [0.028, 0.082] \\
    Pts      &     50.163 &  47.729 &  2.376 &     0.019 &  0.292 &    [0.426, 4.441] \\
    WS       &      0.898 &   0.776 &  5.387 &  $<$0.001 &  0.662 &    [0.077, 0.165] \\
    LS       &      0.609 &   0.751 & -5.335 &  $<$0.001 &  0.655 &  [-0.195, -0.090] \\
    Pers     &      0.245 &   0.259 & -1.505 &     0.139 &  0.185 &   [-0.033, 0.004] \\
    $\beta$  &      6.754 &   4.082 &  5.404 &  $<$0.001 &  0.664 &    [1.702, 3.640] \\
    $\eta_p$ &      0.643 &   0.551 &  2.846 &     0.007 &  0.350 &    [0.029, 0.157] \\
    $\eta_n$ &      0.738 &   0.784 & -1.516 &     0.120 &  0.186 &   [-0.106, 0.013] \\
    $\kappa$ &     -0.069 &  -0.218 &  3.729 &  $<$0.001 &  0.458 &    [0.071, 0.227] \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Measures of task behavior compared between attentive ($N=301$) and C/IE ($N=85$) participants. Metrics compared using two-tailed, two-sample permutation $t$-test with $df=384$ ($\alpha = 0.05$, not corrected for multiple comparisons). Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
    \label{tab:tabS02}
\end{table}

@@

Data from N=7 participants who completed the experiment were excluded prior to analysis because these participants (all from MTurk) disclosed that they had also completed the same experiment on the other platform. This left a final sample of N=393 participants (MTurk: N=193, Prolific: N=200) for analysis. The demographics of the sample split by labor market is provided in Table \ref{tab:demographics_02}. Participants recruited from MTurk were older on average ($\Delta M = 4.9$ yrs; two-tailed, two-sample $t$-test: $t(391)=4.248$, $p<0.001$, $d = 0.429$, 95\% CI = [2.7, 7.2]) and comprised of fewer women (35.2\% versus 61\%; two-tailed, two-sample proportions test: $z(391)=5.500$, $p<0.001$, $h=0.562$, 95\% CI = [0.182, 0.372]).

\begin{table}[!h]
    \centering
    \small
    \setlength{\tabcolsep}{15pt}
    \begin{tabular}{lrrrr}
        \toprule
        & \multicolumn{2}{c}{MTurk} & \multicolumn{2}{c}{Prolific} \\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        Total & \multicolumn{2}{c}{N=193} & \multicolumn{2}{c}{N=200} \\
        \midrule
        Age & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        18-25   &    11 &   5.7 &     47 &  23.5 \\
        26-35   &    71 &  36.8 &     76 &  38.0 \\
        36-45   &    60 &  31.1 &     41 &  20.5 \\
        46-55   &    29 &  15.0 &     22 &  11.0 \\
        55+     &    22 &  11.4 &     14 &   7.0 \\
        \midrule
        Gender & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Female &      68 &  35.2 &      122 &  61.0 \\
        Male   &     124 &  64.2 &       73 &  36.5 \\
        Other  &       1 &   0.5 &        5 &   2.5 \\
        \midrule
        Ethnicity & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Hispanic or Latino     &    16 &   8.3 &     12 &   6.0 \\
        Not Hispanic or Latino &   177 &  91.7 &    180 &  90.0 \\
        Rather not say         &     0 &   0.0 &      8 &   4.0 \\
        \midrule
        Race & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        American Indian/Alaska Native &     2 &   1.0 &      0 &   0.0 \\
        Asian                         &    15 &   7.8 &     41 &  20.5 \\
        Black or African American     &    13 &   6.7 &     12 &   6.0 \\
        White                         &   156 &  80.8 &    133 &  66.5 \\
        Multiracial                   &     6 &   3.1 &     10 &   5.0 \\
        Rather not say                &     1 &   0.5 &      4 &   2.0 \\
        \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{The demographics of each sample by online labor market.}
    \label{tab:demographics_02}
\end{table}

@@

Prior to the start of the two-step task, participants completed four self-report measures in a randomized order. One was the 14-item seven-up/seven-down scale (7u/7d; \cite{youngstrom_2013_susd-2}), which measures lifetime incidence of depressive and (hypo)mania symptoms. This scale is expected to elicit lower rates of symptom endorsement, thereby resulting in asymmetric (right-skewed) score distributions. Participants also completed a 7-item measure of general anxiety symptoms over the last year (e.g., ``I was overwhelmed by anxiety.''; \cite{watson2022development}). This scale is expected to elicit moderate rates of symptom endorsement, thereby resulting in a symmetric score distribution. We therefore expected the depression and mania measures to be at greater risk for spurious correlations with behavior on the two-step task than the anxiety measure.

@@

\begin{figure}[t!]
    \includegraphics[width=15cm]{../figures/repl_02a.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Raincloud plots of total symptom scores in attentive ($N=338$; red) and C/IE ($N=55$; blue) participants. Each colored dot represents the symptom score for one participant. Black circles: average score within each group (error bars denote 95\% bootstrap confidence interval). Shaded plots: estimated distribution of responses for each group of participants.}
    \label{fig:repl_distributions}
\end{figure}

Previously, we observed a mean-shift in the average level of symptom endorsement for participants suspected of engaging in C/IE responding relative to attentive participants on measures for which the overall rate of symptom endorsement is low. This result was (mostly) replicated in the current dataset. Total scores were noticeably exaggerated in participants suspected of C/IE responding for the symptom measures where overall rates of symptom endorsement were the lowest (e.g., mania; Figure \ref{fig:repl_distributions}, leftmost plot). Where there were higher rates of symptom endorsement overall (e.g., anxiety), the distributions of symptom scores between the two groups of participants were more similar (Figure \ref{fig:repl_distributions}, middle plots). Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the most skewed symptom measures (Table \ref{tab:rep_validation}).

For the personality measures, however, an interesting pattern emerged (Figure \ref{fig:repl_distributions}, rightmost plots). We did not observe a statistically significant mean-shift in total scores for the subscale with the most skewed score distribution (i.e., artistic interests). However, an unexpected and statistically significant mean-shift in the average level of endorsement was observed for the more symmetrically-distributed greed-avoidance subscale. The reason for this finding is unclear. Regardless, this finding presents an opportunity to test for spurious correlations between behavioral and self-report measures in the presence of a mean-shift in scores in the absence of (substantially) skewed score distributions.

\begin{table}[!t]
    \centering
    \small
    \begin{tabular}{lccccccc}
        \toprule
        Subscale & Skew &  Attentive & C/IE & $t$-value & $p$-value & Cohen's $D$ & 95\% CI \\
        \midrule
        Mania                &  1.065 &      3.249 &   6.273 & -6.054 &  $<$0.001 &  0.880 &  [-4.003, -2.045] \\
        Depression           &  0.889 &      5.719 &   6.945 & -1.572 &  0.119 &  0.229 &   [-2.756, 0.303] \\
        Anxiety              &  0.438 &      8.536 &   8.655 & -0.127 &  0.900 &  0.019 &   [-1.950, 1.712] \\
        Artistic interests   & -0.918 &     28.068 &  26.291 &  1.872 &  0.061 &  0.272 &   [-0.083, 3.637] \\
        Greed avoidance      &  0.550 &     11.769 &  16.436 & -4.166 &  $<$0.001 &  0.606 &  [-6.863, -2.472] \\
        \bottomrule
    \end{tabular}
    \caption{Comparison of the self-report total scores between attentive ($N=338$) and C/IE ($N=55$) participants. Scores compared using two-tailed, two-sample permutation $t$-test with $df=391$ ($\alpha = 0.05$, not corrected for multiple comparisons).}    
    \label{tab:rep_validation}
\end{table}

@@

Next, we evaluated the degree of correspondence between behavioral and self-report screening measures to determine whether screening on behavior alone was sufficient to identify and remove careless participants. To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses. First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation (Figure \ref{fig:repl_correspondence}, left panel). After correcting for multiple comparisons, there were a handful of significant correlations between the behavioral and self-report screening measures. Abnormal response times emerged as the metric most correlated with the self-report screening measure. Crucially, as in the original study, the sizes of these observed correlations were roughly half those observed for the correlations between the self-report measures.

\begin{figure}[!t]
    \includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/repl_02b.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Similarity of task and self-report data screening measures. Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures across $N=393$ participants. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; SV = side variability; CV = choice variability; WSLS = win-stay lose-shift rate; RT = suspicious response times. Similarity scores have been thresholded after correcting for multiple comparisons. Numbers denote the strength of statistically significant correlations. Cross-modality correlations between task-behavior (left) and infrequency-item self-report measures (bottom) are in the dashed rectangle.}
    \label{fig:repl_correspondence}
\end{figure}

>>>>

\begin{figure}[H]
    \includegraphics[width=17cm]{../figures/supp_01.png}
    \centering
    \caption{Signed Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions. (A) No Screening = no exclusions ($N=386$). (B) Accuracy Only = exclusions based on chance-level performance in the reversal-learning task ($N=352$). (C) Infrequency Only = exclusions based on invalid or improbable responses to infrequency items ($N=301$). (D) Both Types = exclusions based on the previous two measures ($N=283$). Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons). Black Xs indicate significant correlations ablated under screening. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
    \label{fig:figS01}
\end{figure}

\clearpage
\subsection*{Bootstrapping Analysis}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_02.png}
    \centering
    \caption{The pattern of significant behavior-symptom correlations before (A; $N=386$) and after (B; $N=301$) screening compared to the resulting pattern when random subsets of participants ($N=301$, matched to screening using the infrequency measure) are removed (C). Panels (A) and (B) are reproduced from Figure 4 for convenience. (C) The fraction of significant correlations in 5000 bootstrapped samples. (D) The similarity of the pattern of correlations after removal of random subsets to that before and after screening using the infrequency measure ($N=5000$ bootstrapped samples). Similarity was calculated using the simple matching coefficient. Random removal subsets were significantly more similar to the ``No Screening" than to the ``Infrequency" screening datasets (two-tailed, paired-samples $t$-test: $t = 262.490$, $p < 0.001$, $d = 3.713$, 95\% CI = [0.136, 0.138]).}
    \label{fig:figS02}
\end{figure}

\clearpage
\subsection*{The relationship between sample size and false positive rates generalize to other sets of variables}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_03.png}
    \centering
    \caption{False positive rates for spurious correlations \emph{increase} with sample size. \textit{Left:} Spearman rank correlations and 95\% bootstrap confidence intervals between inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants. The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size. Markers are jittered along the x-axis for legibility. \textit{Right:} False positive rates for inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants. False positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\beta$ and 7-down was statistically significant. The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
    \label{fig:figS03}
\end{figure}

\clearpage
\subsection*{The relationship between sample size and true positive rates for true correlations}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_04.png}
    \centering
    \caption{True correlations are independent of the proportion of C/IE participants in the sample. \textit{Left:} Spearman rank correlations and 95\% bootstrap confidence intervals between learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants. The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size. Markers are jittered along the x-axis for legibility. \textit{Right:} True positive rates for learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants. True positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\kappa$ and GAD-7 was statistically significant. The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
    \label{fig:figS04}
\end{figure}

@@

\subsection*{Posterior predictive checks}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_05.png}
    \centering
    \caption{Posterior predictive checks for the risk-sensitive temporal difference learning model. (A) Observed (black) and predicted (blue) learning curves averaged across the group ($N=375$). (B) Observed versus predicted choice accuracy across participants ($N=375$). (C) Distribution of average predictive density across participants ($N=375$).}
    \label{fig:figS05}
\end{figure}

\clearpage
\subsection*{Participant demographics}
\begin{table}[!h]
    \centering
    \small
    \setlength{\tabcolsep}{15pt}
    \begin{tabular}{ rrrrr }
        \toprule
        & \multicolumn{2}{c}{MTurk} & \multicolumn{2}{c}{Prolific} \\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        Total & \multicolumn{2}{c}{N=186} & \multicolumn{2}{c}{N=200} \\
        \midrule
        Age & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        18-25   &      16 &   8.6 &       78 &  39.0 \\
        26-35   &      76 &  40.9 &       69 &  34.5 \\
        36-45   &      46 &  24.7 &       31 &  15.5 \\
        46-55   &      22 &  11.8 &       13 &   6.5 \\
        55+     &      26 &  14.0 &        9 &   4.5 \\
        \midrule
        Gender & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Female             &    83 &  44.6 &    112 &  56.0 \\
        Male               &   103 &  55.4 &     85 &  42.5 \\
        Other              &     0 &   0.0 &      3 &   1.5 \\
        \midrule
        Ethnicity & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Hispanic or Latino     &    15 &   8.1 &     10 &   5.0 \\
        Not Hispanic or Latino &   168 &  90.3 &    183 &  91.5 \\
        Rather not say         &     2 &   1.1 &      7 &   3.5 \\
        Unknown                &     1 &   0.5 &      0 &   0.0 \\
        \midrule
        Race & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        African American                 &    21 &  11.3 &      7 &   3.5 \\
        Asian                                     &     5 &   2.7 &     53 &  26.5 \\
        White                                     &   151 &  81.2 &    121 &  60.5 \\
        Multiracial                               &     6 &   3.2 &      4 &   2.0 \\
        Rather not say                            &     1 &   0.5 &     12 &   6.0 \\
        \midrule
        Use other platform & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Yes            &      71 &  38.2 &       28 &  14.0 \\
        No             &     115 &  61.8 &      172 &  86.0 \\
        \bottomrule
    \end{tabular}
    \caption{The demographics of each sample by online labor market. On average, the samples were similar though the sample from Mechanical Turk was older (two-tailed, two-sample $t$-test: $t(384)=6.567$, $p<0.001$, $d=0.669$, 95\% CI = [5.4, 10.0]) and comprised of fewer women (two-tailed, two-sample proportions test: $z(384)=2.529$, $p=0.011$, $h=0.258$, 95\% CI = [0.030, 0.228]). Note: the demographics do not include 20 participants excluded for participating in the study twice, once per platform.}
    \label{tab:tabS01}
\end{table}

\clearpage
\subsection*{Careless participants show different behaviors on the reversal learning task}
\begin{table}[H]
    \centering
    \begin{tabular}{lcccccc}
    \toprule
    {} &  Attentive &    C/IE &   $t$-value &   $p$-value &  Cohen's $D$ & 95\% CI \\
    \midrule
    Acc      &      0.587 &   0.532 &  4.008 &  $<$0.001 &  0.492 &    [0.028, 0.082] \\
    Pts      &     50.163 &  47.729 &  2.376 &     0.019 &  0.292 &    [0.426, 4.441] \\
    WS       &      0.898 &   0.776 &  5.387 &  $<$0.001 &  0.662 &    [0.077, 0.165] \\
    LS       &      0.609 &   0.751 & -5.335 &  $<$0.001 &  0.655 &  [-0.195, -0.090] \\
    Pers     &      0.245 &   0.259 & -1.505 &     0.139 &  0.185 &   [-0.033, 0.004] \\
    $\beta$  &      6.754 &   4.082 &  5.404 &  $<$0.001 &  0.664 &    [1.702, 3.640] \\
    $\eta_p$ &      0.643 &   0.551 &  2.846 &     0.007 &  0.350 &    [0.029, 0.157] \\
    $\eta_n$ &      0.738 &   0.784 & -1.516 &     0.120 &  0.186 &   [-0.106, 0.013] \\
    $\kappa$ &     -0.069 &  -0.218 &  3.729 &  $<$0.001 &  0.458 &    [0.071, 0.227] \\
    \bottomrule
    \end{tabular}
    \caption{Measures of task behavior compared between attentive ($N=301$) and C/IE ($N=85$) participants. Metrics compared using two-tailed, two-sample permutation $t$-tests ($df=384$, $\alpha = 0.05$, not corrected for multiple comparisons). Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
    \label{tab:tabS02}
\end{table}

@@

Data from N=7 participants who completed the experiment were excluded prior to analysis because these participants (all from MTurk) disclosed that they had also completed the same experiment on the other platform. This left a final sample of N=393 participants (MTurk: N=193, Prolific: N=200) for analysis. The demographics of the sample split by labor market is provided in Table \ref{tab:S10}. Participants recruited from MTurk were older on average ($\Delta M = 4.9$ yrs; two-tailed, two-sample $t$-test: $t(391)=4.248$, $p<0.001$, $d = 0.429$, 95\% CI = [2.7, 7.2]) and comprised of fewer women (35.2\% versus 61\%; two-tailed, two-sample proportions test: $z(391)=5.500$, $p<0.001$, $h=0.562$, 95\% CI = [0.182, 0.372]).

\begin{table}[!h]
    \centering
    \small
    \setlength{\tabcolsep}{15pt}
    \begin{tabular}{lrrrr}
        \toprule
        & \multicolumn{2}{c}{MTurk} & \multicolumn{2}{c}{Prolific} \\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        Total & \multicolumn{2}{c}{N=193} & \multicolumn{2}{c}{N=200} \\
        \midrule
        Age & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        18-25   &    11 &   5.7 &     47 &  23.5 \\
        26-35   &    71 &  36.8 &     76 &  38.0 \\
        36-45   &    60 &  31.1 &     41 &  20.5 \\
        46-55   &    29 &  15.0 &     22 &  11.0 \\
        55+     &    22 &  11.4 &     14 &   7.0 \\
        \midrule
        Gender & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Female &      68 &  35.2 &      122 &  61.0 \\
        Male   &     124 &  64.2 &       73 &  36.5 \\
        Other  &       1 &   0.5 &        5 &   2.5 \\
        \midrule
        Ethnicity & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Hispanic or Latino     &    16 &   8.3 &     12 &   6.0 \\
        Not Hispanic or Latino &   177 &  91.7 &    180 &  90.0 \\
        Rather not say         &     0 &   0.0 &      8 &   4.0 \\
        \midrule
        Race & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        American Indian/Alaska Native &     2 &   1.0 &      0 &   0.0 \\
        Asian                         &    15 &   7.8 &     41 &  20.5 \\
        Black or African American     &    13 &   6.7 &     12 &   6.0 \\
        White                         &   156 &  80.8 &    133 &  66.5 \\
        Multiracial                   &     6 &   3.1 &     10 &   5.0 \\
        Rather not say                &     1 &   0.5 &      4 &   2.0 \\
        \bottomrule
    \end{tabular}
    \caption{The demographics of each sample by online labor market.}
    \label{tab:S10}
\end{table}

@@

Prior to the start of the two-step task, participants completed four self-report measures in a randomized order. One was the 14-item seven-up/seven-down scale (7u/7d; \cite{youngstrom_2013_susd-2}), which measures lifetime incidence of depressive and (hypo)mania symptoms. This scale is expected to elicit lower rates of symptom endorsement, thereby resulting in asymmetric (right-skewed) score distributions. Participants also completed an alternative 7-item measure of general anxiety symptoms over the last year (e.g., ``I was overwhelmed by anxiety.''; \cite{watson2022development}). This scale is expected to elicit moderate rates of symptom endorsement, thereby resulting in a symmetric score distribution. We therefore expected the depression and mania measures to be at greater risk for spurious correlations with behavior on the two-step task than the anxiety measure.

@@

\begin{figure}[t!]
    \includegraphics[width=15cm]{../figures/repl_02a.png}
    \centering
    \caption{Raincloud plots of total symptom scores in attentive ($N=338$; red) and C/IE ($N=55$; blue) participants. Each colored dot represents the symptom score for one participant. Black circles: average score within each group (error bars denote 95\% bootstrap confidence interval). Shaded plots: estimated distribution of responses for each group of participants.}
    \label{fig:S07}
\end{figure}

Previously, we observed a mean-shift in the average level of symptom endorsement for participants suspected of engaging in C/IE responding relative to attentive participants on measures for which the overall rate of symptom endorsement is low. This result was (mostly) replicated in the current dataset. Total scores were noticeably exaggerated in participants suspected of C/IE responding for the symptom measures where overall rates of symptom endorsement were the lowest (e.g., mania; Figure \ref{fig:S07}, leftmost plot). Where there were higher rates of symptom endorsement overall (e.g., anxiety), the distributions of symptom scores between the two groups of participants were more similar (Figure \ref{fig:S07}, middle plots). Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the most skewed symptom measures (Table \ref{tab:S11}).

For the personality measures, however, an interesting pattern emerged (Figure \ref{fig:S07}, rightmost plots). We did not observe a statistically significant mean-shift in total scores for the subscale with the most skewed score distribution (i.e., artistic interests). However, an unexpected and statistically significant mean-shift in the average level of endorsement was observed for the more symmetrically-distributed greed-avoidance subscale. The reason for this finding is unclear. Regardless, this finding presents an opportunity to test for spurious correlations between behavioral and self-report measures in the presence of a mean-shift in scores in the absence of (substantially) skewed score distributions.

\begin{table}[!t]
    \centering
    \small
    \begin{tabular}{lccccccc}
        \toprule
        Subscale & Skew &  Attentive & C/IE & $t$-value & $p$-value & Cohen's $D$ & 95\% CI \\
        \midrule
        Mania                &  1.065 &      3.249 &   6.273 & -6.054 &  $<$0.001 &  0.880 &  [-4.003, -2.045] \\
        Depression           &  0.889 &      5.719 &   6.945 & -1.572 &  0.119 &  0.229 &   [-2.756, 0.303] \\
        Anxiety              &  0.438 &      8.536 &   8.655 & -0.127 &  0.900 &  0.019 &   [-1.950, 1.712] \\
        Artistic interests   & -0.918 &     28.068 &  26.291 &  1.872 &  0.061 &  0.272 &   [-0.083, 3.637] \\
        Greed avoidance      &  0.550 &     11.769 &  16.436 & -4.166 &  $<$0.001 &  0.606 &  [-6.863, -2.472] \\
        \bottomrule
    \end{tabular}
    \caption{Comparison of the self-report total scores between attentive ($N=338$) and C/IE ($N=55$) participants. Scores compared using two-tailed, two-sample permutation $t$-test with $df=391$ ($\alpha = 0.05$, not corrected for multiple comparisons).}    
    \label{tab:S11}
\end{table}

@@

Next, we evaluated the degree of correspondence between behavioral and self-report screening measures to determine whether screening on behavior alone was sufficient to identify and remove careless participants. To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses. First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation (Figure \ref{fig:S08}, left panel). After correcting for multiple comparisons, there were a handful of significant correlations between the behavioral and self-report screening measures. Abnormal response times emerged as the metric most correlated with the self-report screening measure. Crucially, as in the original study, the sizes of these observed correlations were roughly half those observed for the correlations between the self-report measures.

\begin{figure}[!t]
    \includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/repl_02b.png}
    \centering
    \caption{Similarity of task and self-report data screening measures. Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures across $N=393$ participants. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; SV = side variability; CV = choice variability; WSLS = win-stay lose-shift rate; RT = suspicious response times. Similarity scores have been thresholded after correcting for multiple comparisons. Numbers denote the strength of statistically significant correlations. Cross-modality correlations between task-behavior (left) and infrequency-item self-report measures (bottom) are in the dashed rectangle.}
    \label{fig:S08}
\end{figure}

Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:S08}, right panel). This approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate. Results were largely consistent with the correlation analysis: only a handful of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance. Of the significant cross-modality pairs, the average similarly coefficient was less than 0.4. In other words, when any of these sets of two measures are used to identify the top 10\% of participants most strongly suspected of C/IE responding, they agree on only two out of every five participants. Screening on task behavior alone would fail to identify the majority of participants most likely engaging in C/IE responding.
